\documentclass{beamer}
\usepackage[utf8]{inputenc}

\usetheme{Madrid}
\usecolortheme{default}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{txfonts}
\usepackage{tkz-euclide}
\usepackage{listings}
\usepackage{adjustbox}
\usepackage{array}
\usepackage{tabularx}
\usepackage{gvv}
\usepackage{lmodern}
\usepackage{circuitikz}
\usepackage{tikz}
\usepackage[utf8]{inputenc}

\usetheme{Madrid}
\usecolortheme{default}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{txfonts}
\usepackage{tkz-euclide}
\usepackage{listings}
\usepackage{adjustbox}
\usepackage{array}
\usepackage{tabularx}
\usepackage{gvv}
\usepackage{lmodern}
\usepackage{circuitikz}
\usepackage{tikz}
\usepackage{graphicx}

\setbeamertemplate{page number in head/foot}[totalframenumber]

\usepackage{tcolorbox}
\tcbuselibrary{minted,breakable,xparse,skins}



\definecolor{bg}{gray}{0.95}
\DeclareTCBListing{mintedbox}{O{}m!O{}}{%
  breakable=true,
  listing engine=minted,
  listing only,
  minted language=#2,
  minted style=default,
  minted options={%
    linenos,
    gobble=0,
    breaklines=true,
    breakafter=,,
    fontsize=\small,
    numbersep=8pt,
    #1},
  boxsep=0pt,
  left skip=0pt,
  right skip=0pt,
  left=25pt,
  right=0pt,
  top=3pt,
  bottom=3pt,
  arc=5pt,
  leftrule=0pt,
  rightrule=0pt,
  bottomrule=2pt,

  colback=bg,
  colframe=orange!70,
  enhanced,
  overlay={%
    \begin{tcbclipinterior}
    \fill[orange!20!white] (frame.south west) rectangle ([xshift=20pt]frame.north west);
    \end{tcbclipinterior}},
  #3,
}
\lstset{
    language=C,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue},
    stringstyle=\color{orange},
    commentstyle=\color{green!60!black},
    numbers=left,
    numberstyle=\tiny\color{gray},
    breaklines=true,
    showstringspaces=false,
}
%------------------------------------------------------------
%This block of code defines the information to appear in the
%Title page
\title %optional
{Mobile Scanner}
\date{}
%\subtitle{A short story}

\author % (optional)
{Bhoomika L - EE25BTECH11014\\
Vaishnavi R A - EE25BTECH11059
}

\begin{document}


\frame{\titlepage}
\begin{frame}{Mobile Document Scanner}
\begin{itemize}
    \item We are developing a mobile-based document scanning system that automatically detects and captures documents.
\item The scanner will improve usability by reducing manual capture and allowing quick document digitization.
\item To enhance functionality, we are planning to implement two scanning modes:
\end{itemize}
\begin{enumerate}
\item Continuous Video Mode Scanner
\item Multi-Photo Table Scanner
\end{enumerate}
\end{frame}

\begin{frame}{Two Scanning Modes}
    To make the application more flexible and efficient, the scanner will operate in two different modes depending on the user’s requirement.
    \begin{enumerate}
        \item Continuous Video Mode Scanner
\begin{itemize}
    \item Automatically scans documents from a live camera feed.
\end{itemize}
\item  Multi-Photo Table Scanner
\begin{itemize}
    \item Allows users to capture multiple document images and process them together.
\end{itemize}
    \end{enumerate}
    These two modes provide both real-time scanning and batch document processing.
\end{frame}


\begin{frame}{Continuous Video Mode}
\begin{itemize}
    \item The phone camera continuously captures live video frames.
\item A document detection algorithm identifies the document within the frame.
\item A green rectangle appears when a document is detected.
\item If the document remains stable inside the rectangle for a few seconds, the system automatically captures the image.
\item The captured image is then cropped, enhanced, and saved as a scanned document.

\end{itemize}

Advantages
\begin{itemize}
\item Fast scanning process
\item Minimal user interaction
\item Ideal for scanning single documents quickly
\end{itemize}
\end{frame}

\begin{frame}{Multi-Photo Table Mode}
    \begin{itemize}
\item The user can capture multiple photos of documents.
\item All captured images appear in a preview table/grid view.
\item The system processes each image to:
\begin{enumerate}
    \item Detect document boundaries
\item Crop and straighten the document

\item Apply enhancement filters
\end{enumerate}
\item Users can review, reorder, or delete images before final export.
    \end{itemize}
Advantages
    \begin{itemize}
\item Efficient for scanning multiple pages
\item Suitable for notes, assignments, or multi-page documents
\end{itemize}
\end{frame}

\begin{frame}{System Workflow}
    Continuous Mode
\begin{enumerate}
\item Start camera
\item Detect document edges
\item Show bounding rectangle
\item Auto-capture after stability
\item Process and save scanned document
\end{enumerate}
Multi-Photo Mode
\begin{enumerate}
\item Capture multiple images
\item Display images in a table/grid
\item Process each image
\item Review and edit
\item Export as scanned files
\end{enumerate}
\end{frame}

\begin{frame}{Expected Results}
    \begin{itemize}
        \item Faster and more convenient document scanning

\item Automatic document detection and capture

\item Support for both quick scans and multi-page documents

\item Improved user experience through flexible scanning modes
    \end{itemize}
\end{frame}

\end{document}